Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-24 cav2017/cav2017.tex
line breaks

\usepackage{amssymb}
\usepackage{amsmath}
\setcounter{tocdepth}{3}
\usepackage{graphicx}
\usepackage{tikz}
\usepackage{pgfplots}
\usepackage{framed}
\usepackage{listings}
\usepackage{algorithm,algpseudocode}
\usepackage{microtype}
\usepackage{epstopdf}

@@

\begin{abstract}
This work presents a sound and automated approach to synthesize 
safe digital feedback controllers for physical plants represented 
as linear, time invariant models. Models are described as dynamical 
equations with inputs, evolving over a continuous state space and accounting 
for errors due to the digitalization of signals that are manipulated by the 
controller block. 
The approach works in two stages, leveraging the use of counter-example guided
inductive synthesis (CEGIS) and reachability analysis. The former synthesises a static 
feedback controller that stabilizes the system under some restrictions given by the safety of
the reach space. The latter verifies its potential safety by means of either of the following 
approaches: forward reachability analysis via unfolding of the dynamics or invariant set 
generation via abstract acceleration; if the 
verification step fails, we loop back to seek an 
alternative controller benefiting from the obtained counterexamples 
to safety using solution generalization and abstraction refinement.
We are able to efficiently synthesize stable and safe controllers
considering a set of intricate physical plant models taken from the digital
control literature.
\keywords{
State-space dynamical models of physical systems; 
Digital controllers; 
Analogue-to-digital converters; 
Time sampling; 
quantization; 
Fixed-point arithmetic; 
CEGIS; 
safety requirements. 
}
\end{abstract}

@@

\begin{enumerate}
\item In this paper we extend the problem of digital control synthesis from a transfer function representation into a state space representation.
This entails the verification of safety properties in addition to the already existing stability conditions which is a much harder problem.
\item To achieve this, we develop two approaches and compare them, the first relying on a non-deterministic simulation of the system and a completeness proof, whilst the second leverages on the concepts of abstraction and acceleration to increase speed whilst retaining soundness.
\item We develop a solution generalization algorithm for the first approach and an abstraction refinement for the second, both of which improve the performance of the CEGIS loop. 
\item We develop a model for different sources quantization and their effect on the state space progression, for which we find safe bounds that ensure the safety of our controllers in a hybrid continuous-digital domain.
\end{enumerate}

@@

There are two different problems that arise from FWL semantics.  The first
is the error in the dynamics caused by the inability to represent the exact
state of the physical system, while the second relates to rounding errors
during computation.  In~\cite{fialho1994stability}, a stability measure
based on the error of the digital dynamics ensures that the deviation
introduced by FWL does not make the digital system unstable.  A more recent
approach~\cite{DBLP:journals/automatica/WuLCC09} uses $\mu$ calculus to
directly model the digital controller so that the selected parameters are
stable by design.  The analyses
in~\cite{DBLP:conf/hybrid/RouxJG15,DBLP:conf/hybrid/WangGRJF16} rely on an
invariant computation on the discrete system dynamics using Semi-Definite
Programming (SDP).  While the former uses BIBO properties to determine
stability, the latter uses Lyapunov-based quadratic invariants.  In both
cases, the SDP solver uses floating-point arithmetic and soundness is
checked by bounding the error.  An alternative approach is taken
by~\cite{park2016scalable}, where the verification of given control code is
performed against a known model by extracting an LTI model of the code
through symbolic execution.  In order to account for rounding errors, an
upper bound is introduced in the verification phase.
The work in \cite{picasso2003stabilization,picasso2002construction} introduces
attractive invariant sets as a mechanism to bound the quantization error effect
on stabilisation as an invariant set that always converges toward the controllable
set. In a similar fashion, \cite{liberzon2003hybrid} evaluates the dynamics of the
quantization error and bounds its trajectory to a known region over a finite
period of time. This technique works for both linear and non-linear systems.

>>>>

\usepackage{amssymb}
\usepackage{amsmath}
\setcounter{tocdepth}{3}
\usepackage{graphicx}
\usepackage{tikz}
\usepackage{pgfplots}
\usepackage{framed}
\usepackage{listings}
\usepackage{algorithm,algpseudocode}
\usepackage{microtype}
\usepackage{epstopdf}
\usepackage{cite}

@@

\begin{abstract}
%
This work presents a sound and automated approach to synthesize safe digital
feedback controllers for physical plants represented as linear, time
invariant models.  Models are described as dynamical equations with inputs,
evolving over a continuous state space and accounting for errors due to the
digitalization of signals that are manipulated by the controller block.  The
approach works in two stages, leveraging the use of counter-example guided
inductive synthesis (CEGIS) and reachability analysis.  The former
synthesises a static feedback controller that stabilizes the system under
some restrictions given by the safety of the reach space.  The latter
verifies its potential safety by means of either of the following
approaches: forward reachability analysis via unfolding of the dynamics or
invariant set generation via abstract acceleration; if the verification step
fails, we loop back to seek an alternative controller benefiting from the
obtained counterexamples to safety using solution generalization and
abstraction refinement.  We are able to efficiently synthesize stable and
safe controllers considering a set of intricate physical plant models taken
from the digital control literature.
%
\keywords{
State-space dynamical models of physical systems; 
Digital controllers; 
Analogue-to-digital converters; 
Time sampling; 
quantization; 
Fixed-point arithmetic; 
CEGIS; 
safety requirements. 
}
\end{abstract}

@@

\begin{enumerate}
%
\item In this paper we extend the problem of digital control synthesis from a transfer function representation into a state space representation.
This entails the verification of safety properties in addition to the already existing stability conditions which is a much harder problem.
%
\item To achieve this, we develop two approaches and compare them, the first relying on a non-deterministic simulation of the system and a completeness proof, whilst the second leverages on the concepts of abstraction and acceleration to increase speed whilst retaining soundness.
%
\item We develop a solution generalization algorithm for the first approach and an abstraction refinement for the second, both of which improve the performance of the CEGIS loop. 
%
\item We develop a model for different sources quantization and their effect on the state space progression, for which we find safe bounds that ensure the safety of our controllers in a hybrid continuous-digital domain.
%
\end{enumerate}

@@

There are two different problems that arise from FWL semantics.  The first
is the error in the dynamics caused by the inability to represent the exact
state of the physical system, while the second relates to rounding errors
during computation.  In~\cite{fialho1994stability}, a stability measure
based on the error of the digital dynamics ensures that the deviation
introduced by FWL does not make the digital system unstable.  A more recent
approach~\cite{DBLP:journals/automatica/WuLCC09} uses $\mu$ calculus to
directly model the digital controller so that the selected parameters are
stable by design.  The analyses in~\cite{DBLP:conf/hybrid/RouxJG15,
DBLP:conf/hybrid/WangGRJF16} rely on an invariant computation on the
discrete system dynamics using Semi-Definite Programming (SDP).  While the
former uses BIBO properties to determine stability, the latter uses
Lyapunov-based quadratic invariants.  In both cases, the SDP solver uses
floating-point arithmetic and soundness is checked by bounding the error. 
An alternative approach is taken by~\cite{park2016scalable}, where the
verification of given control code is performed against a known model by
extracting an LTI model of the code through symbolic execution.  In order to
account for rounding errors, an upper bound is introduced in the
verification phase.  The work in \cite{picasso2003stabilization,
picasso2002construction} introduces attractive invariant sets as a mechanism
to bound the quantization error effect on stabilisation as an invariant set
that always converges toward the controllable set.  In a similar fashion,
\cite{liberzon2003hybrid} evaluates the dynamics of the quantization error
and bounds its trajectory to a known region over a finite period of time. 
This technique works for both linear and non-linear systems.
